Title

### 2023-10-16 Article.tex
Reorder figures

\begin{table}[H]
\caption{Comparison of the models' error depending on the activation function used.}
\begin{tabular}{lccccc}
\toprule
Activation & Time & $\RMSE$ & $\Delta\RMSE$ & $\MARE$  & $\Delta\MARE$ \\ \midrule
ReLU & 5:14 & 1.171 & 3.422 & 4.575 & 6.350\\ 
Exp & 5:18 & 0.420 & 1.227 & 1.302 & 1.808\\ 
Sigmoid & 5:14 & 0.427 & 1.247 & 0.952 & 1.322\\ 
Tanh & 5:25 & 0.418 & 1.223 & 0.851 & 1.181\\ 
Swish & 5:31 & 0.342 & / &0.720 & / \\ 
Softplus & 5:25 & 0.394 & 1.151 & 1.070 & 1.485\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\caption{Table}
\begin{tabular}{lcccccc}
\toprule
Activation & time & inc & inc/s & $\overline{\varepsilon}^p$ & $\overline{\sigma}$ & $T$\\ \midrule
ReLU & 915 & 1247899 & 1364 & 0.787 & 128.4 & 1071.1 \\
Exp & 998 & 1250145 & 1253 & 0.787 &122.5 &1070.5 \\
Sigmoid & 1089 & 1251869 & 1150 & 0.787 & 126.8 & 1071.1 \\
Tanh & 1202 & 1253740 & 1043 & 0.786 & 125.2 & 1070.6 \\ 
Swish & 1322 & 1246006 & 943 & 0.789 & 123.7 & 1071.0 \\
Softplus & 1795 & 1245146 & 694 & 0.783 & 125.2 & 1070.2 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\caption{Comparison of the models' error depending on the activation function used.}
\begin{tabular}{lccccc}
\toprule
Activation & Time & $\RMSE$ & $\Delta\RMSE$ & $\MARE$  & $\Delta\MARE$ \\ \midrule
Sigmoid & 5:14 & 0.427 & 1.247 & 0.952 & 1.322\\ 
Tanh & 5:25 & 0.418 & 1.223 & 0.851 & 1.181\\ 
ReLU & 5:14 & 1.171 & 3.422 & 4.575 & 6.350\\ 
Softplus & 5:25 & 0.394 & 1.151 & 1.070 & 1.485\\
Swish & 5:31 & 0.342 & / &0.720 & / \\ 
Exp & 5:18 & 0.420 & 1.227 & 1.302 & 1.808\\ 
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\caption{Table}
\begin{tabular}{lcccccc}
\toprule
Activation & time & inc & inc/s & $\overline{\varepsilon}^p$ & $\overline{\sigma}$ & $T$\\ \midrule
Sigmoid & 1089 & 1251869 & 1150 & 0.787 & 126.8 & 1071.1 \\
Tanh & 1202 & 1253740 & 1043 & 0.786 & 125.2 & 1070.6 \\ 
ReLU & 915 & 1247899 & 1364 & 0.787 & 128.4 & 1071.1 \\
Softplus & 1795 & 1245146 & 694 & 0.783 & 125.2 & 1070.2 \\
Swish & 1322 & 1246006 & 943 & 0.789 & 123.7 & 1071.0 \\
Exp & 998 & 1250145 & 1253 & 0.787 &122.5 &1070.5 \\
\bottomrule
\end{tabular}
\end{table}
